\hypertarget{introduction-and-goals}{%
\section{1 Introduction and Goals}\label{section-introduction-and-goals}}

\subsection{Overview}
This project focuses on developing a \textbf{Webshop system} for \textbf{LowTech GmbH} using \textbf{cloud computing}. The objective is to create a \textbf{fully functional e-commerce platform} that is \textbf{scalable, highly available, and responsive}. The system follows a \textbf{Three-Tier Architecture} and is deployed on \textbf{Microsoft Azure}, leveraging cloud services for hosting, storage, and computing power.

\subsection{Project Scope and Requirements}
The Webshop system is designed to meet the following key requirements:

\begin{itemize}
    \item \textbf{High Availability:} The system should have a \textbf{99.99\% uptime}, ensuring minimal downtime.
    \item \textbf{Scalability:} It should dynamically scale to handle increased user traffic.
    \item \textbf{User-Friendly Interface:} The frontend should be \textbf{fast, responsive, and accessible on multiple devices}.
    \item \textbf{Separation of Concerns:}
    \begin{itemize}
        \item \textbf{Frontend (User Interface):} Built using \textbf{Next.js} and \textbf{Tailwind CSS}.
        \item \textbf{Backend (Logic and APIs):} Implemented using \textbf{Python Flask}, providing business logic and API endpoints.
        \item \textbf{Database (Data Storage):} Uses \textbf{Microsoft Azure SQL Database} for structured storage of product, order, and inventory data.
    \end{itemize}
    \item \textbf{Cloud-Based Deployment:} The system is hosted on \textbf{Microsoft Azure}, using its cloud services for computation and storage.
    \item \textbf{Payment System Integration:} The Webshop integrates with \textbf{Stripe API} for payment processing.
    \item \textbf{Modern Development Practices:} The project follows \textbf{best practices}, including \textbf{GitHub version control} and \textbf{CI/CD pipelines}.
\end{itemize}

\subsection{Quality Goals}
The system prioritizes the following \textbf{quality attributes}:

\begin{enumerate}
    \item \textbf{Availability and Reliability:} Ensuring \textbf{99.99\% uptime} with \textbf{Azure Load Balancer and failover mechanisms}.
    \item \textbf{Scalability and Performance:} Supporting \textbf{horizontal scaling} using \textbf{Azure Container Apps}.
    \item \textbf{Security and Compliance:} Protecting data using \textbf{Azure’s encryption and identity management}.
    \item \textbf{Maintainability and Extensibility:} Using \textbf{modular architecture} to facilitate future improvements.
    \item \textbf{User Experience and Accessibility:} Delivering a \textbf{smooth and optimized shopping experience} across different devices.
\end{enumerate}

\subsection{Stakeholders}
The key stakeholders in the project are:

\begin{table}[h]
\centering
\begin{tabular}{|l|l|l|}
\hline
\textbf{Role} & \textbf{Who They Are} & \textbf{What They Expect} \\ \hline
\textbf{CEO} & LowTech GmbH CEO & A modern, reliable cloud-based Webshop. \\ \hline
\textbf{Development Team} & Project Team & Implementing the Webshop with cloud best practices. \\ \hline
\textbf{End Users} & Customers & A fast and smooth shopping experience. \\ \hline
\textbf{Cloud Provider} & Microsoft Azure & Hosting, scaling, and security management. \\ \hline
\end{tabular}
\caption{Stakeholders and their expectations}
\label{tab:stakeholders}
\end{table}
