\hypertarget{section-technical-risks}{%
\section{9 Risks and Technical Debts}\label{section-technical-risks}}

\textbf{Contents}

This section lists the identified technical risks and technical debts for the Webshop system, ordered by priority, to ensure proactive management and system reliability. The risks and debts focus on scalability, security, reliability, and maintainability, reflecting the system’s cloud-based architecture and payment integration.

\textbf{Motivation}

``Risk management is project management for grown-ups'' (Tim Lister, Atlantic Systems Guild.) This motto underscores the importance of systematically detecting and evaluating risks and technical debts in the Webshop’s architecture. These insights are crucial for management stakeholders, such as project managers and product owners, to plan mitigation strategies and ensure the system’s success in a cloud-based, e-commerce context.

\textbf{Form}

The technical risks and debts are presented in a bulleted list, ordered by priority, with descriptions, priorities, and suggested measures to minimize, mitigate, or avoid risks or reduce technical debts.

\begin{itemize}
  \item \textbf{Scalability Limits Under Peak Load (High Priority)}: The Webshop may struggle to handle sudden spikes in traffic (e.g., 1,000 concurrent users during a sale) if Azure’s auto-scaling or Stripe’s transaction processing capacity is underestimated, potentially leading to performance degradation or downtime.  
    \textit{Measures}: Conduct load testing with Azure’s monitoring tools (e.g., Azure Monitor) to validate scalability, optimize Azure auto-scaling policies, and verify Stripe’s plan supports high transaction volumes.

  \item \textbf{Security Vulnerabilities in Payment Integration (Medium Priority)}: Improper configuration of Stripe’s API or Azure’s security settings could expose payment data or user information to breaches, violating privacy regulations or user trust.  
    \textit{Measures}: Implement regular security audits, use Azure’s security features (e.g., Key Vault), and follow Stripe’s security best practices, including PCI DSS compliance.

  \item \textbf{Downtime Due to Azure Service Outages (Medium Priority)}: Reliance on Azure’s infrastructure poses a risk of downtime if Azure experiences regional outages or if geo-redundancy isn’t configured properly, affecting the 99.9\% uptime goal.  
    \textit{Measures}: Configure Azure’s geo-redundant backups and disaster recovery options, monitor Azure SLAs (e.g., 99.95\%–99.99\% uptime), and implement failover strategies.

  \item \textbf{Limited Frontend Maintainability Due to Rapid Prototyping (Low Priority)}: The Next.js frontend, developed quickly with React Context and Tailwind CSS, may have tightly coupled components or inconsistent code patterns, making future updates time-consuming.  
    \textit{Measures}: Refactor critical components to improve modularity, document code patterns, and adopt a style guide for Tailwind CSS and React.

  \item \textbf{Basic Authentication in Admin Module (Low Priority)}: The current authentication for the admin dashboard (e.g., username/password in local storage) lacks robust security (e.g., OAuth, Azure AD), creating a debt needing production upgrades.  
    \textit{Measures}: Plan to integrate Azure Active Directory or OAuth for secure authentication, replacing the basic implementation in future iterations.
\end{itemize}