\hypertarget{introduction-and-goals}{%
\section{Introduction and Goals}\label{section-introduction-and-goals}}

\subsection{Overview}
This project focuses on developing a webshop system for the LowTech GmbH using cloud computing. The objective is to create a fully functional e-commerce platform that is scalable, highly available, and responsive. The system follows a Three-Tier Architecture and is deployed on Microsoft Azure, leveraging cloud services for hosting, storage, and computing power.

\subsection{Project Scope and Requirements}
The Webshop system is designed to meet the following key requirements:

\begin{itemize}
    \item \textbf{High Availability}: The system should have a 99.9\% uptime, ensuring minimal downtime.
    \item \textbf{Scalability}: It should dynamically scale to handle increased user traffic.
    \item \textbf{User-Friendly Interface}: The frontend should be fast, responsive, and accessible on multiple devices.
    \item \textbf{Separation of Concerns}:
    \begin{itemize}
        \item \textbf{Frontend (User Interface)}: Built using Next.js and Tailwind CSS.
        \item \textbf{Backend (Logic and APIs)}: Implemented using Python Flask, providing business logic and API endpoints.
        \item \textbf{Database (Data Storage)}: Uses Microsoft Azure SQL Database for structured storage of product, order, and inventory data.
    \end{itemize}
    \item \textbf{Cloud-Based Deployment}: The system is hosted on Microsoft Azure, using its cloud services for computation and storage.
    \item \textbf{Payment System Integration}: The Webshop integrates with Stripe API for payment processing.
    \item \textbf{Modern Development Practices}: The project follows best practices, including GitHub version control.
\end{itemize}

\subsection{Quality Goals}
The system prioritizes the following quality attributes:

\begin{enumerate}
    \item \textbf{Availability and Reliability}: Ensuring 99.9\% with Azure Load Balancer and failover mechanisms.
    \item \textbf{Scalability and Performance}: Supporting horizontal scaling using Azure Container Apps.
    \item \textbf{Security and Compliance}: Protecting data using Azure’s encryption and identity management.
    \item \textbf{Maintainability and Extensibility}: Using modular architecture to facilitate future improvements.
    \item \textbf{User Experience and Accessibility}: Delivering a smooth and optimized shopping experience across different devices.
\end{enumerate}

\subsection{Stakeholders}
The key stakeholders in the project are:

\begin{center}
    
    \begin{table}[h]
        \centering
        \begin{tabular}{|p{0.2\textwidth}|p{0.2\textwidth}|p{0.6\textwidth}|}
            \hline
            \textbf{Role} & \textbf{Who They Are} & \textbf{What They Expect} \\ \hline
            \textbf{CEO} & LowTech GmbH CEO & A modern, reliable cloud-based Webshop. \\ \hline
            \textbf{Development Team} & Project Team & Implementing the Webshop with cloud best practices. \\ \hline
            \textbf{End Users} & Customers & A fast and smooth shopping experience. \\ \hline
            \textbf{Cloud Provider} & Microsoft Azure & Hosting, scaling, and security management. \\ \hline
        \end{tabular}
        \caption{Stakeholders and their expectations}
        \label{tab:stakeholders}
    \end{table}
\end{center}
